Human Capital Model

### 2015-02-09 paper.tex
Update paper

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}                     %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

@@

\subsection{Literature Review}
\label{sec:literature-review}

\begin{itemize}
\item
\item
\item
\end{itemize}

\section{Terminology}
\label{sec:terminology}

\begin{itemize}
\item
\item
\item
\end{itemize}

@@

In this part, we buid a people model to evaluate an employee in four
aspects, in terms of \textbf{Quantitative Management Performance} ---
work achievement, work ability, work attitude and potential. These
four aspects are supposed to be quantized according to annual
evaluation based on performance as judged by the supervisor and we
take these independent variables as $A_{ac_i}$, $A_{ab_1}$, $A_{at_i}$
and $A_{po_i}$ for each employee $i$. For each of the four parameters,
it goes from 0 to 1. The statues are used for calculating the
probability that employee can promote. Meanwhile, they influence
leaving probability and team cohesiveness as well.

@@

The main part of our model is the algorithm which controls the
behavior of employees. According to assumption 1 and assumption 2, we
have the methodology as follow:

\begin{itemize}
\item [\textit{step 1}]
\end{itemize}

@@

\begin{equation}
\begin{cases}
  \lambda_1 \sum_{i=1}^{370}(1-p_i)=10.9\% \times 370 \times 1.5\% \\
  \lambda_2 \sum_{i=1}^{370}s_i=2.2\% \times 370 \times 1.5\% \\
  l_i3=1.5 \% \times 75.4 \%
\end{cases}
\end{equation}

Thus we can use equation (4) to calculate the churn rate $l_i$.

The second part of the model is promotion model aimed to predict the
promotion condition.We define the promotion rate of an employee i as
$p_i$ to evaluate the probability to promote.As a matter of fact,if
there is a vacancy, judging if an employee suits the site involves
work experience and ability.It is essential that he is supposed to
have several years of work experience according to issue 6.If an
employee satisfies the experience condition,it turns out to think
about his ability.Since in people model,each employee's ability is
evaluated by a parameter $A_{D_i}$. For each level of position,it has
an ability standard,as shows in Figure[]. The ability of an employee
are supposed to reach the four standard parameters
respectively,otherwise its $p_i$ is 0.For those who reach the
standard, the promotion probability can be calculated by the equation:
$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ is
employee who have probability to promote.

@@

\subsection{Analysis for Task 5}
\label{sec:analysis-for-task-5}

@@

@@

@@

@@

@@

\bibitem{}

>>>>

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}                     %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{booktabs}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

@@

Problem C describe ICM as an orginaization of 370 people on human
capital. The company is facing some issues. ICM tend to make a
positive work atmosphere to gain the loyalty of an employee in their
early time.The churn of an some employee makes effect on productivity
and emotion on other employee. Lower quality employees often stay with
the company for a full career. The churn rate is 18\% per year and
mid-level positions suffer high  churn rate, even twice the average
rate of the rest of the company. HR prefer matching employees to the
right position. It only provides promotion opportunity for those who
have several years of work experience. ICM usually has only 85\% of
its 370 positions filled at any time and HR office is actively hiring
about 8\%-10\% of the ICM positions. The CEO salary is approximately
10 times the median of the salaries of all the employees, compared to
hundreds of times the median as found in many companies.

There are several tasks we need to finish according to our model:

\begin{itemize}
\item Build a Human Capital network model of ICM organization’s
  personnel situation.

\item Identify dynamic processes within the Human Capital network,
  which includes orginizatinal churn and direct and indirect effects on
  the organization’s productivity.

\item Analyze your organization’s budget requirements over the next 2
  years.

\item Judge if ICM could sustain its 80\% full status for positions if
  the annual churn rate for all positions goes to 25\% and 35\%
  respectively. Calculate the costs of these higher turnover rates and
  describe the indirect effects of these high churn rates.

\item Simulate the impact of 30\% churn in both junior managers and
  experienced supervisors, if other churn values remain at 18\%.It
  assumes that there is no external recruiting and ICM promote only
  qualified employees for the next two years.

\item Connect our Human Capital network to other organizational
  network layers such as information flow, trust, influence, and
  friendship that the other offices of ICM are considering building.
\end{itemize}

@@

In this part, we buid a people model to evaluate an employee in four
aspects, in terms of \textbf{Quantitative Management Performance} ---
work achievement, work ability, work attitude and potential. These
four aspects are supposed to be quantized according to annual
evaluation based on performance as judged by the supervisor and we
take these independent variables as $A_{ac_i}$, $A_{ab_i}$, $A_{at_i}$
and $A_{po_i}$ for each employee $i$. For each of the four parameters,
it goes from 0 to 1. The statues are used for calculating the
probability that employee can promote. Meanwhile, they influence
leaving probability and team cohesiveness as well.

@@

First, we explain the model of promotion aimed to predict the
promotion probability. We define the promotion rate of $i$ as
$p_i$ to evaluate the probability to promote. As a matter of fact, if
there is a vacancy, judging if an employee suits the site involves
work experience and ability. It is essential that he is supposed to
have several years of work experience according to issue 6. If an
employee satisfies the experience condition, it turns out to think
about his ability. Since in Human Performance Model, each employee's
ability is evaluated by a parameter $A_{D_i}$. For each level of
position, it has an ability standard, as shows in Table[]. The ability
of an employee are supposed to reach the four standard parameters
respectively, otherwise its $p_i$ is 0. For those who reach the
standard, the promotion probability can be calculated by the equation:
$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ represent
employee who have probability to promote.

According to assumption 1 and assumption 2, from $t$ to $t+1$, the
model update once according to the following rules:

\begin{itemize}
\item [\textit{step 1}] Promotion: If there's a vacancy in superior
  and $i$ has the ability to occupy this position, let $L_{i+1,t} =
  L_{i,t}+1$ with probability mentioned above and build edges between
  $i$ and his new colleagues.
\item [\textit{step 2}] Churn: If $i$ isn't promoted, he will have the
  probability to churn with a churn rate $l$.
\item [\textit{step 3}] Stay: If $i$ hasn't been promoted or churned,
  he will keep his job and do nothing.
\end{itemize}

@@

\begin{equation}
\label{lambda}
\begin{cases}
  \lambda_1 \sum_{i=1}^{370}(1-p_i) & =10.9\% \times 370 \times 1.5\% \\
  \lambda_2 \sum_{i=1}^{370}s_i & =2.2\% \times 370 \times 1.5\% \\
  l_{i3} & =1.5 \% \times 75.4 \%
\end{cases}
\end{equation}

Thus we can use Equation\ref{lambda} to calculate the churn rate $l_i$.

@@

\subsection{Analysis for Task 5}
\label{sec:analysis-for-task-5}
a

@@

As the HR manager faces many problems such as identifying those that
are likely to churn and maximizing employees' knowledge and
abilities, we explain our further improved model.

@@

A worker is more likely to churn if he or she was connected to other
former employees who have churned. So there are two kinds of people
who should be highly paid attention to and incented.

First, we should pay attention to those who have more friends than
others. Because of their wide connection with other employees, the
consequence of their churn may be destructive, which cause many
friends' churn.

Second, we focus on those having more friends who have churned
during the past year. This kind of people have a great probability to
churn because of the influence of others.

We choose one sample in our simulations and 50 people in this sample
to explain our incentive mechanism.

\begin{figure}[htb]
  \centering
  \includegraphics[width=7cm]{p1.eps}
  \includegraphics[width=7cm]{p2.eps}
  \caption{employees should be pay attention
    to}\label{incentive-mechanism}
\end{figure}

In Figure\ref{incentive-mechanism}, as we can see, each vertex
represents an employee, each full line represents a relation between 2
employees, each imaginary line represent an relation between person
who is on the job and person who churn. There are 5
employees in left graph we should pay attention to which are
43, 97, 123, 265 and 301 because they have more full lines than
others. There are 6 employees in the right graph we should pay
attention to which are 154, 175, 181, 182, 235 and 255 because they
have more imaginary lines than others.

We provide incentives to these employees which will decrease their
probabilities to churn.

At time $t$, we choose top 10\% of the employees which have the
properties above and decrease their churn rate by 50\%. As shown in
Figure\ref{}, the churn rate decrease rapidly.

@@

We consider different abilities of different employees. As we have an
annual evaluation based on performance for each employee and each
division or office has it's necessarily needed abilities, we can match
employees with their most suitable position.

Because the evaluation is given annually, we reassign employees
annually according to their abilities and the formula below:

\begin{equation}
m_{i,j} =
{(A_{ac_i}-B_{ac_j})}^2 + {(A_{ab_i}-B_{ab_j})}^2 + {(A_{at_i}-B_{at_j})}^2
+ {(A_{po_i}-B_{po_j})}^2
\end{equation}

where $B_{ac_j}$, $B_{ab_j}$, $B_{at_j}$, $B_{po_j}$ represent the
abilities needed for position $j$.

Defining $x_{ij}=\begin{cases} 1 , & \mbox{reassign employee } i
  \mbox{ to position } j \\ 0,&\mbox{otherwise} \end{cases}$, we can
describe this problem as a mathematical programming problem:

\begin{equation}
  \begin{split}
  \min&\sum_{i=1}^n\sum_{j=1}^m m_{ij}x_{ij} \\
  s.t.& \sum_{j=1}^m x_{ij}=1, i=1,2,\ldots,n \\
  &\sum_{i=1}^n x_{ij} \le1,j=1,2,\ldots,m \\
  &x_{ij}=0 \mbox{or} 1,i=1,2,\ldots,n,j=1,2,\ldots,m
  \end{split}
\end{equation}

We can solve this problem via Kuhn–Munkres algorithm [Harold Kuhn and
James Munkres 1957] whose time complexity is $O(n^4)$.

We reassign them once a year according to their
evaluation. Figure\ref{reassign} shows productivity with reassignment
and without reassignment. We can find that the productivity increase
rapidly after reassign employees, which means reassignment truly help
with productivity of the company.

\begin{figure}[center]
  \centering

  \caption{Productivity-Time Curve}\label{reassign}
\end{figure}

@@

This part shows how our model connects to other organizational network
layers such as information flow, trust, influence, and
friendship. Number the layers from 0 to
k. $$G^\alpha=(V^\alpha,E^\alpha), \alpha=1,2,\ldots,k$$ Each
$E^\alpha$ is colored by a specific color. $G^0$ reprensents the
network we built before, $G^1$, $G^2, \ldots ,G^k$ represent the other layers added.

Still, in each network layer $G_\alpha$, $N_i$ represents emploee
$i$. The edge $e_{ij}$ connects between two nodes $N_i$ and
$N_j$. Each edge has a value $w_{ij}^\alpha$ proving the weight of
edge $e_{ij}^\alpha$, positive correlated to the strength of
connection between two employees in network layers $\alpha$. Then we
connect these network layers together to built a general network
$G_e=(V, E, C)$, V is node set, C is color set, $E\subst V\times
V\times C$ is edge set. In the general model, different layers effects
each other. Take for example, if the friendship between employee $i$
and employee $j$ is deeper, with other conditions the same,their
information flow is more fluent. $w_{ij}^\alpha$ is changing with time
flows and G_e is a dynamic network.

However, human capital network make the maily effect on other network
layers. In the general network, if an empolyee churns or is
reassigned, the edge related to him will change. That is,
$w_{ij}^\alpha$ get a new value for all $\alpha$. Hence, human capital
network takes the lead in this effort.

@@

\bibitem{} Huang Y. A Study of the Performance Assessment of State-owned Power Enterprisees[D]. Tianjing University, 2010.

\bibitem{} Journal T E D O T. The Investigation Report of the Condition of employee churn in 2011[J]. China New Time, 2012(2).

\bibitem{} Zhang J. The Empirical Research of the Factors effecting employee churn in Resource-oriented Enterprise in Yuncheng,Shandong [D]. Southerneast University, 2014.

\bibitem{} MEJNewman. The Structure and Function of Complex Networks[D]. University of Michigan, 2003.

\bibitem{} Fang J, Zheng Z, Bi Q, etal. A Brand-new
  Interdisciplinary Science: Network Science (Part One)[J]. Progress in Physics, 2007, 27(3).

\bibitem{} Fang J, Zheng Z, Bi Q, etal. A Brand-new
  Interdisciplinary Science: Network Science (Part Two)[J]. Progress in Physics, 2007, 27(4).
